\section{Introduction}
  The popularity of blockchain protocols in recent years has stretched their
  performance exposing a number of scalability considerations. In particular,
  Bitcoin and related blockchain protocols exhibit very high latency (e.g.\
  Bitcoin has a latency of 1h~\cite{bitcoin}) and a very low throughput (e.g.,
  Bitcoin can handle at most 7 transactions per second~\cite{scaling}), both
  significant shortcomings that jeopardize wider use and adoption and are to a
  certain extent inherent~\cite{scaling}. To address these considerations a
  prominent approach is to optimistically handle payments via a ``Payment
  Channel Network'' (PCN) (see, e.g.,~\cite{DBLP:conf/fc/GudgeonMRMG20} for a
  survey). Payments over a PCN happen \emph{off-chain}, i.e.\ without adding any
  transactions to the underlying blockchain. They only use the blockchain as an
  arbiter in case of dispute.

The key primitive of PCN protocols is a payment channel. Two parties initiate
the channel by locking some funds on-chain and subsequently exchange direct
messages to update the state of the channel. The key feature is that state
updates are not posted on-chain and hence they remain unencumbered by the
performance limitations of the underlying blockchain protocol. Given this
primitive, multiple overlapping payment channels can be combined and form the
PCN.

Closing a channel is an operation that involves posting the state of the channel
on-chain. Closing should be efficient, i.e.\ needing $O(1)$ on-chain
transactions, independent of the number of payments that have occured off-chain.
It is also essential that any party can unilaterally close a channel as
otherwise a malicious counterparty (i.e.\ the other channel participant) could
prevent an honest party from accessing their funds. This functionality however
raises an important design consideration: how to prevent malicious parties from
posting old states of the channel.
%
Addressing this issue can be done with some suitable use of transaction
``timelocks'', a feature that prevents a transaction or a specific script from
being processed on-chain prior to a specific time (measured in block height).
%
For instance, diminishing transaction timelocks facilitated the Duplex
Micropayment Channels (DMC)~\cite{decker} at the expense of bounding the overall
lifetime of a channel. Using script timelocks, the Lightning Network
(LN)~\cite{lightning} provided a better solution that enabled channels staying
open for an arbitrary duration: the key idea was to duplicate the state of the
channel between the two counterparties, say Alice and Bob, and facilitate a
punishment mechanism that can be triggered by Bob whenever Alice posts an old
state update and vice-versa. The script timelocking is essential to allow an
honest counterparty some time to act.

Interconnecting channels in LN enables any two parties to transmit funds
to each other as long as they can find a route of payment channels that connects
them. The downside of this mechanism is that it requires the direct involvement
of all the parties along the path for each payment. Instead, ``virtual payment
channels'', suggest the more attractive approach of putting a one-time off-chain
initialization step to set up a virtual payment channel, which subsequently can
be used for direct payments with complexity ---in the optimistic case---
independent of the length of the path. When the virtual channel has exhausted
its usefulness, it can be closed off-chain if the involved parties cooperate.
Initial constructions for virtual channels essentially capitalized on the extended functionality of Ethereum, e.g.,
Perun~\cite{perun} and GSCN~\cite{DBLP:conf/ccs/DziembowskiFH18}, while more
recent work~\cite{9519487} brought them closer to
Bitcoin-compatibility (by leveraging adaptor
signatures~\cite{DBLP:journals/iacr/AumayrEEFHMMR20}).

A virtual channel constructor can be thought of as an \emph{operator} over the
underlying primitive of a state channel. We can identify three natural
desiderata for this operator.

\begin{itemize}
\item Recursive. A recursive virtual channel constructor can operate over
channels that themselves could be the results of previous applications of the
operator. This is important in the context of PCNs since it allows building
virtual channels on top of pre-existing virtual channels, allowing the channel
structure to evolve dynamically.
\item Variadic. A variadic virtual channel constructor can virtualize any number
of input state channels directly, i.e.\ without leveraging recursion. This is
important in the context of PCNs since it enables applying the operator to build
virtual channels of arbitrary length, without the undue overhead of opening,
managing and closing multiple virtual channels only to use the one at the
``top'' of the recursion.
\item Symmetric. A symmetric virtual channel constructor offers setup and
closing operations that are symmetric in terms of cost between the two
``endpoints'' or the ``intermediaries'' (but not a mix of both) for the
optimistic and pessimistic execution paths. Importantly, this ensures that no party is worse-off or better-off after an application of the operator in terms of accessing the basic functionality of the channel. 
\end{itemize}

The endpoints are the two parties that share the channel, while intermediaries are
the parties of any of the underlying channels.

We note that recursiveness, while identified already as an important design
property~\cite{DBLP:conf/ccs/DziembowskiFH18}, has not been achieved for Bitcoin-compatible channels
(it was achieved only for DMC-like fixed lifetime channels in~\cite{10.1007/978-3-030-65411-5_18} and left as an open question for LN-type channels in~\cite{9519487}).
The reason behind this are the severe limitations imposed by the scripting language of Bitcoin-compatible systems.
With respect to the other two properties, observe that successive applications
of a recursive {\em binary} virtual channel operator to make it variadic will
break symmetry (since the sequence of operator applications will impact the
participants' functions with respect to the resulting channel). This is of
particular concern since most previous virtual channel constructors proposed are
binary~\cite{DBLP:conf/ccs/DziembowskiFH18,9519487,10.1007/978-3-030-65411-5_18}.

\paragraph{Our Contributions.} We present the first Bitcoin-suitable
recursive virtual channel constructor that supports channels
with an indefinite lifetime. In addition, our constructor, Elmo (named after St.
Elmo's fire), is variadic and symmetric. In our constructor, both optimistic and
pessimistic execution paths are optimal in terms of round complexity: issuing
payments between the two endpoints requires just three messages of size
independent of the length of the channel, closing the channel cooperatively
requires at most three messages from each party while
closing the channel unilaterally requires up to two on-chain transactions for
any involved party (endpoint or intermediary) that can be submitted
simultaneously, also independent of the channel's length. Our
construction is also compatible with the current version of any blockchain that
supports Turing-complete smart contracts, such as
Ethereum~\cite{wood2014ethereum}.

We achieve the above by leveraging a sophisticated virtual channel setup
protocol which, on the one hand, enables endpoints to use an interface that is
invariant between on-chain and off-chain (i.e.\ virtual) channels,
while on the other, parties can securely close the channel cooperatively
off-chain, or instead opt for unilateral on-chain closing, following an arbitrary
activation sequence. The latter is achieved by enabling anyone to
become an initiator towards closing the channel, while subsequent respondents, following the activation sequence, can choose the right action to successfully complete the closure process by posting a single transaction each.

  We formally prove the security of the constructor protocol in the Universally
  Composable security (UC)~\cite{uc} setting; our ideal functionality is global,
  according to the definition of~\cite{DBLP:conf/tcc/BadertscherCHTZ20}. The
  construction relies on the \texttt{ANYPREVOUT} signature type (slated for
  inclusion in the next Bitcoin update\footnote{\url{https://anyprevout.xyz/}}), which does not sign the hash of the
  transaction it spends, therefore allowing for a single pre-signed transaction
  to spend any output with a suitable script. We conjecture that, if
  \texttt{ANYPREVOUT} is unavailable, no efficient virtual channel constructor
  protocol over Bitcoin can be built. More specifically, if any such protocol
  (i) offers an efficient closing operation (i.e.\ with $O(1)$ on-chain
  transactions) and (ii) has parties store the channel state as transactions and
  signatures in their local storage, then each party will need exponentially
  large space in the number of intermediaries. Note that the second protocol
  requirement is natural, since, to our knowledge, all trustless layer $2$
  protocols over Bitcoin require all implicated protocol parties to actively
  sign off every state transition and locally store the relevant transactions
  and signatures of their counterparties, thus ensuring their ability to
  unilaterally exit later.
