\section{Preliminaries}
  \subsection{Universal Composition Framework}
  In this work we embrace the Universal Composition (UC) framework~\cite{uc} to
  model parties, network interactions, adversarial influence and corruptions, as
  well as formalise and prove security.

  UC closely follows and expands upon the paradigm of simulation-based
  security~\cite{DBLP:books/sp/17/Lindell17}. For a particular real world
  protocol, the main goal of UC is allow us to provide a simple ``interface'',
  the ideal world functionality, that describes what the protocol achieves in an
  ideal way. The functionality takes the inputs of all protocol parties and
  knows which parties are corrupted, therefore it normally can achieve the
  intention of the protocol in a much more straightforward manner. At a high
  level, once we have the protocol and the functionality defined, our goal is to
  prove that no probabilistic polynomial-time (PPT) Interactive Turing Machine
  (ITM) can distinguish whether it is interacting with the real world protocol
  or the ideal world functionality. If this is true we then say that the
  protocol UC-realises the functionality.

  The principal contribution of UC is the following: Once a functionality that
  corresponds to a particular protocol is found, any other higher level protocol
  that internally uses the former protocol can instead use the functionality.
  This allows cryptographic proofs to compose and obviates the need for
  re-proving the security of every underlying primitive in every new application
  that uses it, therefore vastly improving the efficiency and scalability of the
  effort of cryptographic proofs.

  An Interactive Turing Instance (ITI) is a single instantiation of an ITM. In
  UC, a number of ITIs execute and send
  messages to each other. At each moment only one ITI is executing (has the
  ``execution token'') and when it sends a message to another ITI, it transfers
  the execution token to the receiver. Messages can be sent either locally
  (inputs, outputs) or over the network.

  The first ITI to be activated is the environment \environment. This can be an
  instance of any
  PPT ITM. This ITI encompasses everything that happens around the protocol
  under scrutiny, including the players that send instructions to the protocol.
  It also is the ITI that tries to distinguish whether it is in the real or the
  ideal world. Put otherwise, it plays the role of the distinguisher.

  After activating and executing some code, \environment may input a message to
  any party. If this execution is in the real world, then each party is an ITI
  running the protocol \prot. Otherwise if the execution takes place in the
  ideal world, then each party is a dummy that simply relays messages to the
  functionality \func. An activated real world party then follows its code,
  which may instruct it to parse its input and send a message to another party
  via the network.

  In UC the network is fully controlled by the so called adversary \adversary,
  which may be any PPT ITI. Once activated by any network message, this machine
  can read the message contents and act adaptively, freely communicate with
  \environment bidirectionally, choose to deliver the message right away, delay
  its delivery arbitrarily long, even corrupt it or drop it entirely. Crucially,
  it can also choose to corrupt any protocol party (in other words, UC allows
  adaptive corruptions). Once a party is corrupted, its internal state, inputs,
  outputs and execution comes under the full control of \adversary for the rest
  of the execution. Corruptions take place covertly, so other parties do not
  necessarily learn which parties are corrupt. Furthermore, a corrupted party
  cannot become honest again.

  The fact that \adversary controls the network in the real world is modelled by
  providing direct communication channels between \adversary and every other
  machine. This however poses an issue for the ideal world, as \func is a single
  party that replaces all real world parties, so the interface has to be adapted
  accordingly. Furthermore, if \func is to be as simple as possible, simulating
  internally all real world parties is not the way forward. This however may
  prove necessary in order to faithfully simulate the messages that the
  adversary expects to see in the real world. To solve these issues an ideal
  world adversary, also known as simulator \simulator, is introduced. This party
  can communicate freely with \func and completely engulfs the real world
  \adversary. It can therefore internally simulate real world parties and
  generate suitable messages so that \adversary remains oblivious to the fact
  that this is the ideal world. Normally messages between \adversary and
  \environment are just relayed by \simulator, without modification or special
  handling.

  From the point of view of the functionality, \simulator is untrusted,
  therefore any information that \func leaks to \simulator has to be carefully
  monitored by the designer. Ideally it has to be as little as possible so that
  \simulator does not learn more than what is needed to simulate the real world.
  This facilitates modelling privacy.

  At any point during one of its activations, \environment may return a binary
  value (either $0$ or $1$). The entire execution then halts. Informally, we say that \prot
  UC-realises \func, or equivalently that the ideal and the real worlds are
  indistinguishable, if $\forall \text{ PPT } \adversary, \exists \text{ PPT }
  \simulator: \forall \text{ PPT } \environment$, the distance of the
  distributions over the machines' random tapes of the outputs of \environment
  in the two worlds is negligibly small. Note the order of quantifiers:
  \simulator depends on \adversary, but not on \environment.

  \subsection{\ledger Functionality}
  In this work we choose to model the Bitcoin ledger with the \ledger
  functionality as defined in~\cite{BMTZ17} and further refined
  in~\cite{genesis}. \ledger formalizes an ideal data structure that is
  distributed and append-only, akin to a blockchain. Participants can read from
  \ledger, which returns an ordered list of transactions. Additionally a party
  can submit a new transaction which, if valid, will eventually be added to the
  ledger when the adversary decides, but necessarily within a predefined time
  window. This property is named liveness. Once a transaction becomes part of
  the ledger, it then becomes visible to all parties at the discretion of the
  adversary, but necessarily within another predefined time window, and it
  cannot be reordered or removed. This is named persistence.

  Moreover, \ledger needs the \Fclock
  functionality~\cite{DBLP:conf/tcc/KatzMTZ13}, which models the notion of time.
  Any \Fclock participant can request to read the current time (which is
  initially 0) and inform \Fclock that her round is over. \Fclock increments the
  time by one once all parties have declared the end of their round. We further note that both
  \ledger and \Fclock are global functionalities~\cite{globaluc} and therefore
  can be accessed directly by the environment.

  \subsection{Modelling time}
  The protocol and functionality defined in this work do not use \Fclock
  directly. Indeed, the only notion of time in our work is provided by the
  blockchain height, as reported by \ledger. We therefore omit it in the
  statement of our lemmas and theorems for simplicity of notation; it should
  normally appear as a hybrid together with \ledger.

  Our protocol is fully asynchronous, i.e., the adversary can delay any network
  message arbitrarily long. The protocol is robust against such delays, as an
  honest party can unilaterally prevent loss of funds even if some of its
  incoming and outgoing network messages are dropped by \adversary, as long as
  the party has input-output communication with the ledger. We also note that,
  following the conventions of single-threaded UC execution model, the duration of local
  computation is not taken into account in any way (as long as it does not
  exceed its polynomial bound).
